\Large{Learning to Pivot with Adversarial Networks}

### 2016-10-31 tex/paper.tex
save
some trimming for better layout

We do not expect that we will be able to find a function $f$ that simultaneously
minimizes the classification loss $L_f$ and is pivotal. Thus, we need to optimize
the hyperparameter $\lambda$ of Eqtn.~\ref{eqn:vf-lambda} with respect to
a higher-level objective. In this case, the natural higher-level context is a
hypothesis test of a null hypothesis with no $Y=1$ events against an
alternate hypothesis that is a mixture of $Y=0$ and $Y=1$ events.
In the absence of systematic uncertainties optimizing $L_f$ simultaneously
optimizes the power of a classical hypothesis test in the Neyman-Pearson sense.
When we include systematic uncertainties we will need to balance the
classification performance against the robustness to uncertainty in $Z$.
Since we are still performing a hypothesis test against the null, we only
wish to impose the pivotal property on $Y=0$ events. Furthermore,
we use the Approximate Median Significance (AMS), that was used
in the Higgs boson machine learning challenge that is a natural generalization
of the power of a hypothesis test when systematic uncertainties are taken into account
(see Eqn.~20 of \citep{adam2014higgs}).

@@

As  Fig.~\ref{fig:physics-ams} illustrates, without adversarial training (at
$\lambda=0|Z=0$ when building a classifier at the nominal value $Z=0$ only, or
at $\lambda=0$ when building a classifier on data sampled from $p(X,Y,Z)$), the
AMS peaks at $7$. By contrast, as the pivotal constraint
is made stronger (for $\lambda > 0$) the AMS peak moves higher, with a maximum
value around  $7.8$ for $\lambda=10$. In other words, trading classification
accuracy for robustness to pileup results in a net
benefit in terms of the power of the resulting hypothesis test. Setting $\lambda$ too high however
(e.g. $\lambda=500$) results in a decrease of the maximum AMS, by
focusing the capacity of $f$ too strongly on independence with $Z$, at the expense of
classification accuracy. As demonstrated in this example, optimizing $\lambda$
gives us a principled and effective approach to control the tradeoff between
classification accuracy and robustness that ultimately maximizes the
power of the enveloping hypothesis test.
%significance by desensitizing
%the classifier output $f(X;\theta_f)$ in the most beneficial way.

>>>>

We do not expect that we will be able to find a function $f$ that simultaneously
minimizes the classification loss $L_f$ and is pivotal. Thus, we need to optimize
the hyperparameter $\lambda$ of Eqn.~\ref{eqn:vf-lambda} with respect to
a higher-level objective. In this case, the natural higher-level context is a
hypothesis test of a null hypothesis with no $Y=1$ events against an
alternate hypothesis that is a mixture of $Y=0$ and $Y=1$ events.
In the absence of systematic uncertainties, optimizing $L_f$ simultaneously
optimizes the power of a classical hypothesis test in the Neyman-Pearson sense.
When we include systematic uncertainties we need to balance the
classification performance against the robustness to uncertainty in $Z$.
Since we are still performing a hypothesis test against the null, we only
wish to impose the pivotal property on $Y=0$ events. Furthermore,
we use the Approximate Median Significance (AMS), that was used
in the Higgs boson machine learning challenge that is a natural generalization
of the power of a hypothesis test when systematic uncertainties are taken into account
(see Eqn.~20 of \citep{adam2014higgs}).

@@

As  Fig.~\ref{fig:physics-ams} illustrates, without adversarial training (at
$\lambda=0|Z=0$ when building a classifier at the nominal value $Z=0$ only, or
at $\lambda=0$ when building a classifier on data sampled from $p(X,Y,Z)$), the
AMS peaks at $7$. By contrast, as the pivotal constraint
is made stronger (for $\lambda > 0$) the AMS peak moves higher, with a maximum
value around  $7.8$ for $\lambda=10$. In other words, trading classification
accuracy for robustness to pileup results in a net
benefit in terms of the power of the resulting hypothesis test. Setting $\lambda$ too high however
(e.g. $\lambda=500$) results in a decrease of the maximum AMS, by
focusing the capacity of $f$ too strongly on independence with $Z$, at the expense of
classification accuracy. As demonstrated in this example, optimizing $\lambda$
gives us a principled and effective approach to control the tradeoff between
accuracy and robustness that ultimately maximizes the
power of the enveloping hypothesis test.
%significance by desensitizing
%the classifier output $f(X;\theta_f)$ in the most beneficial way.
